PEACE: {\underline P}arallel {\underline E}nvironment for {\underline A}ssembly and {\underline C}lustering of Gene {\underline E}xpression

### 2010-11-22 peace/papers/NAR_web_server_2009/paper.tex
Adding Trey's thesis

\mc{We tested the three tools on short-read data using the \metasim\/
  tool of {\it Richter et al.} \cite{Richter2008}.  Encoded into
  \metasim\/ are sequence generation and error models corresponding to
  several technologies, including the 454 short-read technology
  (producing reads ranging in size from 200bp to 370bp with a mean of
  250bp and a standard deviation of 17bp), and the Illumina short-read
  technology (producing reads of exactly 62bp).  Experiments were run
  using two sets of \wcd\/ parameters (the default parameters, and
  setting window size to 75 and threshold to 75 -- thus matching the
  equivalent \peace\/ parameters), and using default values
  of \capthree.  Only with \peace\/ were we able to get reasonable
  results, seeing a sensitivity of 0.871 for the 454 reads and
  0.583 or the shorter Illumina reads, a Jaccard Index of 0.809 and
  0.372 respectively, and other comparably figures.  (See Table~S3 in
  the Supplementary Materials.)  In short, \peace performs quite well
  for 454 reads and provides some useful information for Illumina
  reads, while \wcd\/ and \capthree\/ are unable to produce working
  results.}

>>>>

We tested the tools on short-read data using the \metasim\/ tool
of {\it Richter et al.} \cite{Richter2008}.  Encoded into \metasim\/
are sequence generation and error models corresponding to several
technologies, including the 454 short-read technology (producing reads
ranging in size from 200bp to 370bp with a mean of 250bp and a
standard deviation of 17bp), and the Illumina short-read technology
(producing reads of exactly 62bp).  In the 454 experiments \peace\/
achieved a sensitivity of 0.871, an 89.7\% improvement in sensitivity
over \wcd\/ and a 193\% improvement in sensitivity over \tgicl, with
comparable values for the Jaccard Index.  \wcd\/ was unable to handle
the Illumina data, while \peace\/ sensitivity, at a value of 0.384,
was nearly twice as good as TGICL.  (For more details, see Table~S3
in the Supplementary Materials.)  In short, \peace\/ performs quite
well for 454 reads and provides some useful information for Illumina
reads, with considerably better results than \wcd\/ or \tgicl\/.
